Estimating duration in the presence of misclassification

### 2024-07-29 introduction.tex
Christl typo

The surveillance systems set-up in response to SARS-CoV-2 were on a scale never previously seen.
The main data sources informing the response to the SARS-Cov-2 epidemic in England were based on: community testing, severe events, seroprevalence surveys, and prevalence surveys.
Each of these data sources have strengths and weaknesses, see \textcite{royalSocietyRnumber} and references therein for further details on each of these data sources.

>>>>

The surveillance systems set-up in response to SARS-CoV-2 were on a scale never previously seen.
The main data sources informing the response to the SARS-Cov-2 epidemic in England were based on: community testing, severe events, seroprevalence surveys, and prevalence surveys.
Each of these data sources has strengths and weaknesses, see \textcite{royalSocietyRnumber} and references therein for further details on each of these data sources.
